Curiosity-Driven Development of Tool Use Precursors: a Robotic Model

### 2016-01-20 cogsci2016/paper.tex
eps

			The agent also needs an interest model that chooses which regions of the motor or sensory space to explore.
			If the agent chooses goals in the motor space and explores them it is called Motor Babbling, and if it chooses the goals to explore in the sensory space, this is Goal Babbling.
			To choose the goals in this space of interest, different strategies are possible. 
			The simplest one is to draw random goals in this space, but strategies based on the learning progress in different regions of the space have been shown more efficient in [ref].
			This strategies are called active as the agent autonomously drives its exploration towards regions of the space that are both reachable and learnable. 
			We use the SAGG-RIAC architecture \cite{baranes_active_2013} where the space of interest is the sensory space (Goal Babbling) and that incrementally splits this space into subregions where the learning progress 
			is different.

@@

	\begin{figure*}[ht]
		\centering
		\subfloat[$Hand$]{\includegraphics[width=4.5cm]{./include/xp1-explo-hand.png}}
		\subfloat[$Stick_1$]{\includegraphics[width=4.5cm]{./include/xp1-explo-stick_1.png}}
		\subfloat[$Stick_2$]{\includegraphics[width=4.5cm]{./include/xp1-explo-stick_2.png}}\\
		\subfloat[$Object$]{\includegraphics[width=4.5cm]{./include/xp1-explo-obj.png}}
		\subfloat[$Boxes$]{\includegraphics[width=4.5cm]{./include/xp1-explo-box.png}}
		\caption{Exploration of sensory spaces.}
		\label{res_explo}
	\end{figure*}

>>>>

			The agent also needs an interest model that chooses which regions of the motor or sensory space to explore.
			If the agent chooses goals in the motor space and explores them it is called Motor Babbling, and if it chooses the goals to explore in the sensory space, this is Goal Babbling.
			To choose the goals in this space of interest, different strategies are possible. 
			The simplest one is to draw random goals in this space, but strategies based on the learning progress in different regions of the space have been shown more efficient in [ref].
			This strategies are called active as the agent autonomously drives its exploration towards regions of the space that are both reachable and learnable. 
			We use the SAGG-RIAC architecture \cite{baranes_active_2013} where the space of interest is the sensory space (Goal Babbling) and that incrementally splits this space into subregions where the learning progress 
			is different. 
			The learning progress is here computed as the absolute derivative of the reaching competence. 
			This competence associated to a sensory goal is minus the distance between the goal and the sensory point.

@@

	\begin{figure*}[ht]
		\centering
		\subfloat{\includegraphics[width=14cm]{./include/xp1-explo-legend.eps}}\\
		\vspace{-0.3cm}
		\subfloat[$Hand$]{\includegraphics[width=3.5cm]{./include/xp1-explo-hand.eps}}
		\subfloat[$Stick_1$]{\includegraphics[width=3.5cm]{./include/xp1-explo-stick_1.eps}}
		\subfloat[$Stick_2$]{\includegraphics[width=3.5cm]{./include/xp1-explo-stick_2.eps}}
		\subfloat[$Object$]{\includegraphics[width=3.5cm]{./include/xp1-explo-obj.eps}}
		\subfloat[$Boxes$]{\includegraphics[width=3.5cm]{./include/xp1-explo-box.eps}}
		\caption{Exploration of sensory spaces.}
		\label{res_explo}
	\end{figure*}
